Predicting Evaluation Prices of Danish Real Estate Property

### 2019-08-29 Opsætningexam/DraftExam.tex

\documentclass[12pt,a4paper]{article}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\onehalfspacing
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pst-tree}
\usepackage{tikz}
\usetikzlibrary{trees}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{enumerate} 
\usepackage{amssymb}
\usepackage{csquotes}
\usepackage{fancyhdr}
\usepackage{times}
\usepackage{fancyhdr}
\usepackage[bottom]{footmisc}
\pagestyle{fancy}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{lscape}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\DeclareMathSizes{12}{12}{10}{10}
\interfootnotelinepenalty=10000
\usepackage{dsfont}
\usepackage{mathtools}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{multirow, booktabs}
\usepackage[final]{pdfpages}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{booktabs,siunitx}
\usepackage{float}
\lhead{}
\rhead{}
\chead{}

@@

\tableofcontents
\newpage
\section{Introduction}
This report depicts a research performed regarding active Danish real-estate property valuations from 2016-2019. Since 2011, the yearly number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years (Danmarks Statistik, 2018).  The price of real estate properties is also rising through 2019 (Danmarks Statistik, 2019). Although this generally depicts a willingness of buyers to pay more for real-estate property, and higher valuations from agents, a closer analysis of current and active valuations add a local view of which conditions contribute to the valuation of a real-estate property. \newline
\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=1]{123.png}
\end{figure}

@@

The valuations included in the research are collected from one of Denmarks largest online real-estate websites named Boliga.dk. The Boliga data contains approximately 66,000 dkk. active offerings with valuations ranging from 15,000 to 85 million dkk. This research paper intends to analyze real estate price valuations and which effects geo- and sociodemographic criteria affect valuations, using machine learning models. Our research questions is as follows: 
Which features are most relevant for predicting evaluations of real estate properties in Denmark?

This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the machine learning model. Also, a section regarding the choice and optimization of machine learning models is included, where the intention is to provide insights on our progress on finding the optimal model. As a result, a preferable machine learning model is chosen with a discussion of its usability.

@@

@@

No informed consent has been obtained from the users of the site, prompting us to consider the consequences of the lack thereof, as informed consent is paramount to the proper, ethical conduct in social science. However, sometimes, as in this instance, informed consent can be logistically impossible to collect from all participants in the study. Salganik mentions that informed consent for everything is an ideal, but in practice impossible to obtain and researchers should instead strive to follow an alternative rule, that he describes as: "some form of consent for most things." \footnote{Salganik, Matthew J. (2019) \textit{Bit by Bit Bit - Social research in the digital age.} p.281} Adhering to this, more complex  understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context. Boliga responded positively to our inquiry, which we took as informed consent from a third party on behalf of the participating users in our study.\newline

@@

The scraping process was conducted on Friday the 23rd of August 2019. We had advised Boliga of our intent to collect data from their website via our scraper in an effort to identify ourselves and our intent\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism. Global Investigative Journalism Network.}}. In order to scrape the data of interest we familiarized ourselves with the HTML-structure of Boliga. On the basis of these insights we constructed a code, which were able to scrape every page, containing information pertaining the currently listed real-estates on Boliga. The scraper requested all information available from each individual page, which surmounted to 1,319 URL requests. \newline

@@

Continuous: & basementSize, buildYear, Ejerudgift, lotSize	, price, rooms, size  \\	

@@

@@

\paragraph{\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk}\newline}
\href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns distances from a given address, to conveniences such as supermarkets, hospitals and schools.   
The scraping of \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} was achieved by writing a function that took in the GPS-coordinates gathered from Boliga. It constructed a URL (65,950 URL request), \textcolor{red}{which was scraped and the json response was returned as a dictionary of distances to the points of interest. The values from each key in the dictionary was then extracted as a new column in a Pandas DataFrame}.\newline
As Jupyter performs poorly at running long asynchronous tasks and estimated a running time of 18 hours this procedure was run in Visual Studio.
 \vspace*{10px} \newline
\textit{Features obtained:}\newline
\begin{tabular}{c c}
Distances to: & lake, forest, doctor, supermarket,	school, daycare, hospital, train \\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad &  pharmacy, library, coast, junction \\	
\end{tabular}\newline

\paragraph{Social and economic factors\newline}
Social and economic factors on municipality level is collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and  
\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively. These factors include income, reported crime, level of highest completed education etc. These are transformed into ratios, by taking the total population in a given municipality into account.   
 \vspace*{5px} \newline
\begin{tabular}{c c}
\textit{Features obtained:}: & Relativ Ledighed, Grundskole, Gymnasiale uddannelser \\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad \quad & Erhvervsfaglige uddannelser,	 KVU, 	MVU, Bacheloruddannelser  \\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad \quad & LVU, Kommunal\_gennemsnitsinkomst\_2017, Total\_reported\\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad \quad & Population\_in\_urban\_development  , Socioeconomic\_index \\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad \quad & average\_class\_size,	expenses\_sport\_and\_other\_cultural\_activities	  \\	
\end{tabular}\newline 
\begin{tabular}{c c}
\qquad \qquad \qquad \qquad \quad & expenses\_per\_school\_student	   \\	
\end{tabular}\newline 
% 				average_class_size	expenses_sport_and_other_cultural_activities
\subsection{Merging Data}

\subsection{Data Cleaning}

A few of the listed housing, have been listed for over a decade. These are considered outliers, which are overly priced considering their characteristics. The outliers are excluded, because they would otherwise only contribute to further bias of overestimation. The total number of excluded housing are approximately 4000.

\subsection{Descriptive Statistics}
\begin{table}[h!]
\begin{center}
\caption{Key Statistics\label{time}}
\begin{tabular}{| c | c | c | c | c | c |} 
\hline
   & Price & \, Rooms \ & \ $m^2$ \ & Average Municipal Income \\ \hline
   Mean & 2,312,798.00 & \ 4.21 \  & \ 127.82 \ & 312,957.03 \\ \hline
   Std & 2,351,127.00 & 2.12 & 75.67 & 46,095.34 \\ \hline
   Min & 15,000.00 & 0 & 0 & 257,776 \\ \hline
   25\% & 985,000.00 & 3 & 82 & 290,973 \\ \hline
   50\% & 1,695,000.00 & 4 & 123 & 302,153 \\ \hline
   75\% & 2,895,000.00 & 5 & 167 & 318,745 \\ \hline
   Max & 85,000,000.00 & 50 & 2,390 & 583,331 \\ \hline
\end{tabular}
\end{center}
\end{table} 
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{Barplot_Estate2.png} 
  \label{fig:}
\end{figure}

n.b. 0

\subsubsection{The Dataset}
The merged dataset contains 61.618 observations and 37 features.   The features are of both categorical and continuous measures. \newline

\subsubsection{Selecting Features}

\section{Methods}
\subsection{Supervised Machine Learning}
The objective by applying Machine Learning is to train a model that can predict pricing of housing listed in near future.
\textcolor{red}{Two types of predictive models will be used for the sake of returning different outputs: Regression-model to return the pricing as a continuous output.}  
\subsection{Fitting the model}
The potential problems of underfitting and overfitting should be assessed when fitting a model. A model is underfitted if it hardly captures the variation of the sample data. It is then said that the model has \textit{high bias}. A model is overfitted, when it is overly sensitive to the idiosyncrasy of the sample data and captures the variation in too great detail. This problem often comes with the introduction of a sizeable number of features. Overfit models are said to have \textit{high variance}\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}. p.73}. In both cases, the model will generalize poorly. A key step in defining a decent model in machine learning is to find an optimal bias-variance-balance, by tuning the complexity of one’s model. This is done through \textit{regularization}. In this project three different types of regularization are applied; Lasso, Ridge and Elastic net.

\subsubsection{Lasso}
Regularization by Lasso, will penalize complexity of the model by the sum of the absolute value of the coefficients. This penalty will make the model less complex and more appropriate for prediction.  \footnote{Foster, Ian; Rayid Ghani Ron S. Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools} p. 173}\, \footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} p. 332}
\newline Lasso minimizes: $$L_{Lasso}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}|\hat{\beta_j}|\right) \qquad s.t \quad \lambda \geq 0 $$
Another convenient attribute of the Lasso penalty is that some estimates are set equal to zero and thereby produce sparse models\footnote{Hal R. Varian. \textit{Big data: New tricks for econometrics. Journal of Economic Perspectives}. p.19}. Lasso thereby performs the feature selection automatic.   
\subsubsection{Ridge}
The ridge model penalizes with the sum of squared coefficients. Opposed to Lasso, Ridge do not force features to be omitted. Ridge minimizes:
$$L_{Ridge}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$

\subsubsection{Elastic-net}
The Elastic net is a combination of Lasso and Ridge. Elastic net minimizes the function: 
$$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}(\beta)\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right)$$
$$0 \leq \alpha \leq 1 \quad \wedge \quad \lambda \geq 0$$
Where $\alpha$ denotes the relative mixing between Lasso and Ridge.

\subsection{Perfomance, Precision \& Recall}

@@

@@

\newpage
\section{Litterature}
\ Foster, Ian; Rayid Ghani Ron S. Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools}, CRS Press 2017

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\onehalfspacing
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pst-tree}
\usepackage{tikz}
\usetikzlibrary{trees}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{enumerate} 
\usepackage{amssymb}
\usepackage{csquotes}
\usepackage{fancyhdr}
\usepackage{times}
\usepackage{fancyhdr}
\usepackage[bottom]{footmisc}
\pagestyle{fancy}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{lscape}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\DeclareMathSizes{12}{12}{10}{10}
\interfootnotelinepenalty=10000
\usepackage{dsfont}
\usepackage{mathtools}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{multirow, booktabs}
\usepackage[final]{pdfpages}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{booktabs,siunitx}
\usepackage{float}
\usepackage{caption}
\lhead{}
\rhead{}
\chead{Social Data Science, Summer 2019.}

@@

\tableofcontents
\newpage
\section{Introduction}
This report depicts a research performed regarding active Danish real-estate property valuations from 2016-2019. Since 2011, the yearly number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979}{(Danmarks Statistik, 2018)}.  The price of real estate properties is also rising through 2019 \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741}{(Danmarks Statistik, 2019)}. Although this generally depicts a willingness of buyers to pay more for real-estate property, and higher valuations from agents, a closer analysis of current and active valuations add a local view of which conditions contribute to the valuation of a real-estate property. \newline
\newcommand{\source}[1]{\caption*{Source: {#1}} }\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.4]{123.png}
\source{Own creation, with data from \href{https://www.boliga.dk}{Boliga.dk}}
\end{figure}

@@

The valuations included in the research are collected from one of Denmarks largest online real-estate websites named Boliga.dk. The Boliga data contains approximately 66,000 active offerings with valuations ranging from 15,000 to 85 mil.dkk. This research paper intends to analyze real estate price valuations and which effects geo- and sociodemographic criteria affect valuations, using machine learning models. Our research questions is as follows: 
\begin{center}
 \textit{Which features are most relevant for predicting evaluations of real estate properties in Denmark?}
\end{center}
This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the machine learning model. Also, a section regarding the choice and optimization of machine learning models is included, where the intention is to provide insights on our progress on finding the optimal model. As a result, a preferable machine learning model is chosen with a discussion of its usability.

@@

Within data social science there exist widely differing definitions of big data and machine learning. This section seeks to clarify the use of these terms within the scope of this paper.
\paragraph{On big data \& machine learning\newline}
Historically, big data has been a term reserved for data that was unable to be processed by extant software. However, recent increases in computational power has enabled data processing of hitherto unheard of quantities of data\footnote{Lazer, David and Jason Radford (2017) \textit{Data ex Machina. Introduction to Big Data}. Annual Review of Sociology}. Today, big data is no longer too cumbersome to analyse. Matthew Salganik\footnote{Salganik, Matthew J. (2018) \textit{Bit by Bit Bit - Social research in the digital age.}} instead mentions ten typical characteristics of big data. Salganik's tentative definition suggests that big data is not as single entity, but includes many different types of systems. Among the most important features of Salganik's definition of big data is that the data has a high frequency of observations and is continuously being generated. Since the data is always-on it is also drifting, meaning that the structure and population it represents is ever-changing. It is therefore important to understand that big data is not a naturally occurring system, but driven by the engineered purpose of the system. This algorithmic confounding forces the scientist to be careful regarding any observed human behaviour that is extracted from a single digital system.\newline
In the analysis of big data it is often useful to employ machine learning as it can identify and predict various nonlinear relationships in big data sets, that otherwise would remain hidden. Data scientists' have for the most part optimised the predictive capabilities of the algorithm applied, and as a consequence they have often ignored or trivialised machine learning's potential in causal modelling\footnote{Varian. Hal R. \textit{Big data: New tricks for econometrics}}.\newline
The technical and theoretical challenges faced by big data and machine learning research are important to consider, when employing the tools they provide. One of the major discussions revolve around machine learning's predictive capabilities. Chris Anderson\footnote{Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete}} (2008) argues that since the computing power and the scale of data has increased exponentially, our reliance of scientific models could become obsolete. Instead of focusing on the theoretical implications of observations, scientists should, according to Anderson, focus on the statistical outputs: In the age of big data, correlation perhaps should supersede causality and consequently social data scientists should not try to develop coherent models or unified theories to explain a social phenomenon.\newline
However, many social data scientists argue against this point of view. Justin Grimmer\footnote{Grimmer, Justin (2015) \textit{We are all social scientists now: how big data, machine learning, and causal inference work together}} claims, that correlations extracted from big data cannot stand alone. Large quantities of data is not sufficient to make scientifically valid causal inferences. It requires a rigorous research design and clear theoretical assumptions, in order to yield scientifically accurate estimates. Indeed social sciences greatest contribution to big data research, comes from the organized framework provided by rigorously tested theory\footnote{Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data}}.\newline
The contribution from the social sciences to machine learning help create new methods that will be able to utilize the strengths of machine learning to help solve causal inference problems within the framework of a well defined theory\footnote{Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al. (eds) \textit{The Economics of Artificial Intelligence: An Agenda}}. These new approaches could help define what variables to manipulate and how to properly use machine learning within the framework of theoretical assumptions. Ultimately, big data and machine learning could increase the scope of the social scientist's field, not only by delivering new data and methods, but by helping the social scientist to focus on new questions\footnote{Mullainathan, Sendhil, and Jann Spiess (2017) \textit{Machine Learning: An Applied Econometric Approach}}.

@@

No informed consent has been obtained from the users of the site, prompting us to consider the consequences of the lack thereof, as informed consent is paramount to the proper, ethical conduct in social science. However, sometimes, as in this instance, informed consent can be logistically impossible to collect from all participants in the study. Salganik mentions that informed consent for everything is an ideal, but in practice impossible to obtain and researchers should instead strive to follow an alternative rule, that he describes as: "some form of consent for most things." \footnote{Salganik, Matthew J. (2018) \textit{Bit by Bit Bit - Social research in the digital age.} p.303} Adhering to this, more complex  understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context. Boliga responded positively to our inquiry, which we took as informed consent from a third party on behalf of the participating users in our study.\newline

@@

The scraping process was conducted on Friday the 23rd of August 2019. We had advised Boliga of our intent to collect data from their website via our scraper in an effort to identify ourselves and our intent\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism}. Global Investigative Journalism Network.}. In order to scrape the data of interest we familiarized ourselves with the HTML-structure of Boliga. On the basis of these insights we constructed a code, which were able to scrape every page, containing information pertaining the currently listed real-estates on Boliga. The scraper requested all information available from each individual page, which surmounted to 1,319 URL requests. \newline

@@

Continuous: & basementSize, buildYear, ownersExspenses, lotSize	, price, rooms, size  \\	

@@

\end{tabular}
\paragraph{\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk}\newline}
\href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns distances from a given address, to conveniences such as supermarkets, hospitals and schools.   
The scraping of \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} was achieved by writing a function that took in the GPS-coordinates gathered from Boliga. It constructed a URL (65,950 URL request), \textcolor{red}{which was scraped and the json response was returned as a dictionary of distances to the points of interest. The values from each key in the dictionary was then extracted as a new column in a Pandas DataFrame}.\newline
As Jupyter performs poorly at running long asynchronous tasks and estimated a running time of 18 hours this procedure was run in Visual Studio.
\textit{Features obtained:}\newline
Distances to: & lake, forest, doctor, supermarket,	school, daycare, hospital, train \\	

@@

\qquad \qquad \qquad \qquad &  pharmacy, library, coast, junction \\	
\end{tabular}
\paragraph{Social and economic factors\newline}
Social and economic factors on municipality level is collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and  
\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively. These factors include income, reported crime, level of highest completed education etc. These are transformed into ratios, by taking the total population in a given municipality into account.   
 \vspace*{5px} \newline
\textit{Features obtained:}: & unemployment\_relative, primary\_school\_educ, high\_school\_educ \\	
\small (relative to population) & vocational\_educ,	 SHE, 	MHE, bachelors\_degree  \\	
\qquad \qquad \qquad \qquad \quad & LHE, avg\_municipal\_income\_2017, Total\_reported\_crime\\	
\qquad \qquad \qquad \qquad \quad & Population\_in\_urban\_development  , Socioeconomic\_index \\	
\qquad \qquad \qquad \qquad \quad & average\_class\_size,	expenses\_sport\_and\_other\_cultural\_activities	  \\	
\qquad \qquad \qquad \qquad \quad & expenses\_per\_school\_student	   \\	
\small {All educational features are a measure of highest completed education. Furthermore SHE, MHE, LHE are abbreviations of short-, medium- and long-cycle higher education}. 
\normalsize
\subsection{Log Analysis}

\subsection{Merging Data}
Pandas objects can be combined in different ways according to the nature of features in the dataset. Relational database style operations are based on linking keys together, thereby maintaining the relationship between the combined datasets\footnote{McKinney, W. (2018). \textit{Data Wrangling: Join, Combine and Reshape}. p. 231 }

The data collection and scraping process provided a total of 15 Datasets from Boliga, Hvorlangterder, DAWA, the Danish Police, Social- \& Indenrigsministeriet and Danmarks Statistik. This section will describe how each dataset was merged, using pandas relational database styled merge and join operations.

\paragraph{Boliga.dk\newline}
An evaluation of the Boliga datasets features and their ability to support further data collection led to the utilization of the following features:

-	[Longitude, Latitude]: Geographical placements of the properties

-	Municipality: a numeric code for municipalities in Denmark

The Boliga dataset acts as a master dataset and was joined or merged upon throughout the process, and acts as the “left” of all operations. The Longitude and Latitude features serve as specific coordinates for valued properties but are in few cases repetitive regarding different apartments from the same complex. The municipality code was used for translation purposes between the master dataset and other datasets.

\paragraph{DAWA\newline}
The DAWA dataset was scraped with an input of a distinct municipality code from the master dataset, returning a dataframe of municipality names for each code. This dataframe was merged onto the Boliga dataframe as a many-to-one merge with municipality code as the merge keys. The scraped municipality names from DAWA was used as the merge key for all further merges of municipal data.

\paragraph{Danmarks Statistik, Danish Police \& Social og Indenrigsministeriet\newline}
Of the municipality-based data collected, the merging of these to our master dataframe was subsequently performed identically. Every dataset contained a column for unique municipality names and values for the given feature of the dataset. A many-to-one left merge was performed with the master dataframe, using municipality names. The result being a master dataframe containing municipal specific features for properties.

The Danish Police datasets contained totals for different categories of crimes reported within municipalities. These datasets were outer joined with an index set to contain municipality names. Afterwards, the values were added to each other, providing a total of reported crimes within each municipality. The police statistics webpage does not specify whether different types of reported crimes can relate to a single case, but we assessed that the number of crimes reported provides a meaningful feature either way. The dataset containing total reported crimes per municipality, was merged with the master dataset in the same fashion as previous municipality-based features.

\paragraph{Hvorlangterder.dk\newline}
The hvorlangterder scrape provided location specific features, taking an input of Latitude and Longitude coordinates. The scraping function, which was created for returning location-based features, created a column for the row specific values. Therefore, a merge operation was not necessary, but could alternatively have been managed with a one-to-one inner-merge id. As few coordinates regarding apartment properties are repetitive, these are not suitable for merging upon.

\subsection{Data Cleaning}
The scraping of Boliga left us with 65,950 observations. However, big data is often dirty and requires tidying before it can be used in any meaningful statistical context (Salganik 2018). In the following sections we describe our data cleaning efforts. 
\subsubsection{Initial clean-up}
The initial clean-up sorted out rows that contained an illogical value. Here we focused our efforts on the removing any and all observations that contained a municipality code of 0. Additionally, we chose to exclude any real estate valued below 100 DKK, while these listings existed on Boliga's website, they were all listings, where the seller wanted  to sell to the highest bidder. We excluded these listings on the basis that they were unrealistically priced compared to the property's real market value.\newline
Boliga subdivides its listings into ten real-estate types. We chose to exclude the typification "other", as there were only 17 houses listed in the category - too few for training our machine learning model. Furthermore, we also removed any listing without coordinates as these were vital for the scraping process on hvorlangerder.dk.\newline
We dropped all observations with an unreasonably high "liggetid", as we saw these instances to not  represent reasonable pricing or demand. We have thus set an arbitrary limit of 3 years (1,095 days), and omitted any observations that has been on the market for longer than that. This results in the omission of approximately 5\% of our dataset. The highest mean "liggetid" on a municipal level was roughly 600 days, so as not to discriminate against the observations from the municipalities with a longer average 'sales time' we set the cut-off somewhat higher than the highest mean. Another option was to set the limit according to each municipality's mean, a solution that was a bit more time consuming, and would have yielded approximately the same result, hence we opted not to do it.
In figure XX the number of rows dropped at each step of the cleaning can be perused.
\begin{center}
\begin{tabular}{|l|c|}
\hline 
Feature & \emph{n} \\
\hline 
Municipality code & 231 \\ 
\hline 
Price & 11 \\ 
\hline 
Coordinates & 275 \\ 
\hline 
Type & 17 \\ 
\hline 
Liggetid & 3,940\\
\hline 
Total\footnote{"The total is the count of how many rows were dropped. Some rows were missing multiple features.} & 4,332\\
\hline
\end{tabular} 
\end{center}

\subsubsection{Ejerlejlighed's lot size}
Inspecting our data we found that from 8,028 apartments 1,176 of these had a lot size. These listings included the apartment complex' common area, whereas the rest did not. To overcome this discrepancy we chose to set all non-zero values to zero, as not to confuse our model with an inconsistent feature (Raschka \& Mirjalili 2017).

\subsubsection{Final touch-ups}
After merging the housing info with the demographic data and the distances from hvorlangterder.dk, we removed a single duplicate and deleted all columns not relevant for our analysis. After the clean-up of the data we were left with a dataset consisting of 61,618  observations and 37 features and 1 target variable.

\subsection{Descriptive Statistics}
In this section, we will examine the more apparent patterns of our collected data. This is done to familiarize ourselves with the data, before we commence on the analysis.
\subsubsection{Key Statistics}
Some key statistical characteristic is presented in table 1:
\begin{table}[H]
\begin{center}
\caption{Key Statistics\label{time}}
\begin{tabular}{| c | c | c | c | c | c |} 
\hline
   & Price & \, Rooms \ & \ $m^2$ \ & Average Municipal Income \\ \hline
   Mean & 2,312,798.00 & \ 4.21 \  & \ 127.82 \ & 312,957.03 \\ \hline
   Std & 2,351,127.00 & 2.12 & 75.67 & 46,095.34 \\ \hline
   Min & 15,000.00 & 0 & 0 & 257,776 \\ \hline
   25\% & 985,000.00 & 3 & 82 & 290,973 \\ \hline
   50\% & 1,695,000.00 & 4 & 123 & 302,153 \\ \hline
   75\% & 2,895,000.00 & 5 & 167 & 318,745 \\ \hline
   Max & 85,000,000.00 & 50 & 2,390 & 583,331 \\ \hline
\end{tabular}
\end{center}
\end{table} 
Initially, it should be addressed that some of the properties has 0 rooms and consists of 0 $m^2$.  This is due to the fact that we have also included land on which housing has not yet been build. Examining the 25\%-quintile and the 75\%-quintile of the valuation prices, it becomes apparent that there are some substantial outliers both to the cheaper and to expensive side. This is also the case with rooms and $m^2$, where the highest values are sizably higher than the 75\%-quintile. 
It is worth noting, that there is quite a big difference between the lowest average municipal income of DKK 257,776. and the highest of DKK 583,331. This difference becomes further noteworthy when assessing the 75\%-quintile. The difference from the 75\%-quintile to the highest average municipal income is more than 4 times the difference of the 75\%-quintile and the lowest income. The income distribution is visualised in the following figure:
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{Box1.png} 
  \label{fig:}
\end{figure}
The boxplot illustrates that the distribution is heavily left-skewed, where some municipalities has a sizably higher average income than the rest of the Danish municipalities.

\subsubsection{Prices in Municipalities}
We plot the average square meter valuation price in the different municipalities:
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{Box2.png} 
  \label{fig:}
\end{figure}
It becomes apparent that the distribution is quite left-skewed and that there are a few municipalities who’s price per square meter is much higher than the rest of the municipalities. Recalling the geoplot in figure 1, these expensive outliers are heavily concentrated around- and north of Copenhagen. 
The distribution looks similar to that of figure 2 (The previous boxplot), though we cannot declare any correlation between average municipal income and average municipal price per square meter. Nonetheless, it becomes apparent that the valuation price of property is highly discriminated by municipal factors. The scope of this assignment is exactly to examine these factors and attempt to use these to evaluate an unseen, out-of-sample property.

\subsubsection{Property Type}
Another worthwhile consideration is that we have included all types of properties. It would be reasonable to assume that there is an average difference in valuation pricing depending on the type of property. Figure 4 displays the median valuation price for each type:
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{bar1.png} 
  \label{fig:}
\end{figure}
It is interesting to note that the most expensive properties are apartments as opposed to houses. This is not especially surprising though, as it is a well-established trend that real estate prices in major cities are skyrocketing. Refraining from delving deeper into to a discussion of global urbanization, we retain the fact that property type does have an apparently significant effect on valuation pricings on average. We will include the ‘type’ feature in our impending model training to control for this effect.

\subsubsection{The Dataset}
The merged dataset contains 61.618 observations and 37 features.   The features are of both categorical and continuous measures. Skal dette ikke bare op i Merging data?\newline

\section{Methods}
\subsection{Supervised Machine Learning}
The objective by applying Machine Learning is to train a model that are able to make predictions in near future or never seen data. By feeding a model with labeled data as well as data samples, ML will define the algorithms that predicts the best\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}. p. 3}.   This project, implements a ML regression prediction model to predict pricing of housing listed in near future.
\subsection{Fitting the model}
The potential problems of underfitting and overfitting should be assessed when fitting a model. A model is underfitted if it hardly captures the variation of the sample data. It is then said that the model has \textit{high bias}. A model is overfitted, when it is overly sensitive to the idiosyncrasy of the sample data and captures the variation in too great detail. This problem often comes with the introduction of a sizeable number of features. Overfit models are said to have \textit{high variance}\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}. p.73}. In both cases, the model will generalize poorly. A key step in defining a decent model in machine learning is to find an optimal bias-variance-balance, by tuning the complexity of one’s model. This is done through \textit{regularization}. In this project three different types of regularization are applied; Lasso, Ridge and Elastic net.

\subsubsection{Lasso}
Regularization by Lasso, will penalize complexity of the model by the sum of the absolute value of the coefficients. This penalty will make the model less complex and more appropriate for prediction.  \footnote{Foster, Ian; Rayid Ghani Ron S. Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools} p. 173}\, \footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} p. 332}
\newline Lasso minimizes: $$L_{Lasso}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}|\hat{\beta_j}|\right) \qquad s.t \quad \lambda \geq 0 $$
Another convenient attribute of the Lasso penalty is that some estimates are set equal to zero and thereby produce sparse models\footnote{Hal R. Varian. \textit{Big data: New tricks for econometrics}. Journal of Economic Perspectives. p.19}. Lasso thereby performs the feature selection automatic.   
\subsubsection{Ridge}
The ridge model penalizes with the sum of squared coefficients. Opposed to Lasso, Ridge do not force features to be omitted. Instead Ridge penalizes the parameter estimates and decreases them towards zero. Ridge minimizes:
$$L_{Ridge}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$

\subsubsection{Elastic-net}
The Elastic net combines the penalizing terms of Lasso and Ridge, with $\alpha$ defining the relative weights between Lasso and Ridge. Elastic net minimizes the function: 
$$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}(\beta)\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right)$$
$$0 \leq \alpha \leq 1 \quad \wedge \quad \lambda \geq 0$$

\subsection{Selecting Features}
In case regularization is not sufficient to cope with the overfitting of the model. Exclusion of features are a viable approach. With the number of scraped features in this project, taking into consideration. A recurring overfitting of the model would be likely. As a consequence a deliberate exclusion of features of interest will need to be carried out.

@@

Even after regularization, and deliberate exclusion of features. Our model still suffers from overfitting. 

@@

\newpage
\section{Litterature}
\ Foster, Ian; Rayid Ghani Ron S. Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools}, CRS Press 2017 \newline
